\textbf{\supplement}\vskip 2ex \mytitle\vskip 2ex

### 2023-05-12 paper-seb-supplementary-material.tex
Small typos fixed in supplemental material

There was no evidence of any critical assessment of code, suggesting that scientists writing papers take it for granted that their code works as they intend. No competent programmer would take it for granted that their code was correct without following rigorous methods, such as formal methods, regression testing, test driven design, etc. (See the \supplement\ for a list of standard methods.)

>>>>

There was no evidence of any critical assessment of code, suggesting that scientists writing papers take it for granted that their code works as they intend. No competent programmer would take it for granted that their code was correct without following rigorous methods, such as formal methods, regression testing, test driven design, etc (see section \ref{supplementary-best-practice} in this \supplement).
